Dynamic Topic Modeling for Voice Dialogues

### 2024-05-01 paper/main.tex
write topic extraction + exps

\section{PromptTopic}

\subsection{LLM for topic extraction}

\subsection{Stage Evaluation}
As for the quality evaluation of the extracted topics, we will use two metrics: Topic coherence and Topic diversity
\begin{itemize}
    \item \textbf{Topic diversity} \cite{topicdiversity:2019} is a metric that assesses the ratio of unique keywords across all topic representations. This metric is used to measure the capabilities of a topic model covering a wide range of topics. The diversity score is a value between 0 and 1, with a score of 0 indicating repetitive topics and a score of 1 indicating diverse topics.
    \item \textbf{Topic coherence} \cite{topiccoh:2009} is a measure of the degree of interconnection of words within a topic. In our experiments, we employed normalized point-to-point mutual information (PMI) as a metric for thematic consistency. A higher score for a given name indicates greater consistency, with an absolute correlation estimated at 1 point.
    \end{itemize}
\newpage
\chapter{Experiments}

@@

@@

At the text clustering stage, comparisons are made between models of non-alternative baselines, because at this stage we are using a ready-made algorithm and making a minimum of changes.
As for topic extraction, our LLM approach will be compared with BertTopic and LSA.

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{2}{| c |}{Country List} & \multicolumn{3}{| c |}{Country List} &  \multicolumn{3}{| c |}{Country List}  \\
        \hline
        model & dataset & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        bert-base NSP & tiage & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & superseg & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-large NSP & tiage & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & superseg & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{2}{| c |}{Country List} & \multicolumn{3}{| c |}{Country List} &  \multicolumn{3}{| c |}{Country List}  \\
        \hline
        model & dataset & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        bert-base NSP & committee & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & committee & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-large NSP & isci & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & isci & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base NSP & ami & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & ami & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

\section{Topic extraction}

\begin{center}
    \begin{tabular}{ |c|c|c| } 
     \hline
     model & Pk & wd \\ 
     \hline
     bert-base NSP & cell5 & cell6 \\ 
     bert-base CLS & cell8 & cell9 \\ 
     \hline
    \end{tabular}
\end{center}

@@

Summarizing all the results of the article:

The study encompassed a range of approaches to topic modelling, including techniques such as segmentation of dialogues, topic extraction and topic evolution for dynamic topic modelling.
For each of these stages, open source approaches with high reported metrics and open source models were studied.

>>>>

\section{Topic Extraction}

The next stage in the pipeline is topic extraction. At this stage, $n$ topics will be extracted from each segment in the dialogues. 
At this stage, past approaches have used probabilistic or embedding approaches, like BertTopic \cite{berttopic:2022}. 
In our work, we will apply a generative approach using Large Language models, as in PromptTopic \cite{prompttopic:2023}.

We will try several Large Language Models by submitting a dialogue segment as input. The prompt for LLM will look like this:

\begin{lstlisting}
    <|user|> 
    utterance_1
    utterance_2
    ...
    utterance_n. 
    You have dialogue between two people, 
    extract N topic words. 
    <|assistant|>

\end{lstlisting}

where $utterance$ is one phrase of the participant in the dialogue, \\$M$ - is the number of words. The appearance of the keywords <|user|>, <|assistant|> dependes on type of LLM.

\subsection{Stage Evaluation}

As for the quality evaluation of the extracted topics, we will use two metrics: Topic coherence and Topic diversity
\begin{itemize}
    \item \textbf{Topic diversity} \cite{topicdiversity:2019} is a metric that assesses the ratio of unique keywords across all topic representations. This metric is used to measure the capabilities of a topic model covering a wide range of topics. The diversity score is a value between 0 and 1, with a score of 0 indicating repetitive topics and a score of 1 indicating diverse topics.
    \item \textbf{Topic coherence} \cite{topiccoh:2009} is a measure of the degree of interconnection of words within a topic. In our experiments, we employed normalized point-to-point mutual information (PMI) as a metric for thematic consistency. A higher score for a given name indicates greater consistency, with an absolute correlation estimated at 1 point.
\end{itemize}

\chapter{Experiments}

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & null \\ 
            Product Meetings (QMSum) & 137 & 535.6 & null \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & null \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & null \\
            \hline
        \end{tabular}
    \end{center}
\end{table}

@@

At the text clustering stage, comparisons are made between models of non-alternative baselines, because at this stage we are using a ready-made algorithm and making a minimum of changes.
As for topic extraction, our LLM approach will be compared with BertTopic and LSA. \\

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \hline
        model &  Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        bert-base NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

In terms of textual datasets ...

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Product} &  \multicolumn{3}{| c |}{Academic} & \multicolumn{3}{| c |}{Committee} \\
        \hline
        model  & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        bert-base NSP &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1  \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base NSP &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}

Speaking about results on audio corpora ...

\section{Topic extraction}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \hline
        model & TC & TD & TC & TD \\ 
        \hline
        bert-base NSP & c & d & c & d \\ 
        bert-base CLS & c & d & c & d \\ 
        bert-large NSP & c & d & c & d \\ 
        bert-base CLS & c & d & c & d \\ 
        \hline
    \end{tabular}
\end{center}

In terms of textual datasets ...

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Product} &  \multicolumn{2}{| c |}{Academic} & \multicolumn{2}{| c |}{Committee} \\
        \hline
        model  & TC & TD & TC & TD & TC & TD  \\ 
        \hline
        LLaMA2 7b & c & d & c & d & c & d \\ 
        LLaMA3 8b & c & d & c & d & c & d \\ 
        Mistral 7B & c & d & c & d & c & d \\ 
        phi3 & c & d & c & d & c & d \\ 
        bert-base NSP & c & d & c & d & c & d \\ 
        bert-base CLS & c & d & c & d & c & d \\ 
        \hline
    \end{tabular}
\end{center}

Speaking about results on audio corpora ...

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Various approaches for dialogue segmentation, topic mining, and topic evolution have been explored;
    \item The search for suitable text and audio datasets was conducted, and the selected datasets were analysed and preprocessed for experiments at all stages and for the entire pipeline.
    \item In the context of the dialog segmentation stage, the optimal open-source solution was identified and the BERT model was subjected to detailed analysis.  This approach has been prepared and integrated into the general pipeline.
    \item At the topic extraction stage, new approaches utilising generative models were investigated. Furthermore, a range of large language models, including LlaMA and Mistral, were examined, along with novel features that enhance the default architecture of the Transformer.
    \item Topic Evolution
    \item A suitable set of metrics was identified and selected to evaluate the quality of each stage. In order to utilise the metrics, a library with an implementation was Investigated and integrated into pipeline.
\end{itemize}
